Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-08 ProbabilisticCoherence.tex
Updating in Dubai

Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible. A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$. For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The hierarchical structure of the data imply the following holds for all $t$:
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints. For the hierarchy in Figure~\ref{fig1}
$$
  \bm{S} = \begin{pmatrix}
               1& 1 &1 &1  \\
               1 &1 & 0 &0 \\
               0&0  & 1 & 1 \\
               & \multicolumn{2}{c}{\bm{I}_4} &
           \end{pmatrix},
$$
where $\bm{I}_4$ is a $4\times 4$ identity matrix.

@@

It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints. We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature {\em coherence} to describe this property.
%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.

\begin{definition}[Coherent subspace]\label{def:cohspace}
 The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}.
\end{definition}

Also at times is will be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$ in which case we use the notation $s(.)$. Although the codomain of $s(.)$ is $\mathbb{R}^n$ its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.

\begin{figure}[H]
  \begin{center}
    \begin{tikzpicture}[
    >=stealth,
    bullet/.style={
      fill=black,
      circle,
      minimum width=1.5cm,
      inner sep=0pt
    },
    projection/.style={
      ->,
      thick,
      label,
      shorten <=2pt,
      shorten >=2pt
    },
    every fit/.style={
      ellipse,
      draw,
      inner sep=0pt
    }
    ]

    \node at (2,3) {$s$};

    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
    \node at (4.5,1.0) {$\mathfrak{s}$(image of $s$)};
    %\node[bullet,label=below:$f(x)$] at (4,2.5){};

    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
    \draw (4,2.5) ellipse (0.51cm and 1.1cm);

    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
\end{figure}

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  The measure $\breve{\nu}$ is coherent if it has the property
  $$
    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
  $$
\end{definition}
A probabilistic forecast for time $t+h$ is coherent if uncertainty in ${\bm y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.

@@

These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $s(.)$ and may give the impression that the bottom level series play an important role in the definition. However, alternative definitions could be formed using any set of basis vectors that spans $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.

@@

%Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions. According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series. Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.

@@

Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$. Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})={\bm G}{\bm y}+{\bm d}$.
\begin{definition}\label{def:reconpoint}
  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
  \begin{equation}
    \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+{\bm d}\right)\,.
  \end{equation}
\end{definition}

Many choices of $g(.)$ currently extant in the literature including the OLS, WLS and MinT methods are special cases where $s\circ g$ is a projection. These can be defined so that ${\bm G}=\left({\bm R'_{\perp}}{\bm S}\right)^{-1}{\bm R}_{\perp}'$ and ${\bm d}={\bm 0}$. Here, ${\bm R_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$. For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$. In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. For this example, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the OLS method. For the case where ${\bm R}_\perp'\neq{\bm S}$, for example WLS and MinT, there are two possible interpretations. One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$. Alternatively, since ${\bm R}_\perp'$ is usually written in the form ${\bm S}'{\bm W}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm W^{-1/2}}$. A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while and are Table~\ref{table:2} summarises existing reconciliation methods.

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}. Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{figure}
	\input{Figs/pointforerec_schematic.tex}
	\caption{Summary of probabilistic point reconciliation. The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm y}$ onto $\mathfrak{s}$. Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
\end{figure}

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$. For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$. \citet{Wickramasuriya2017} while MinT
minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$. Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series. As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

Before generalising the concept of point reconciliation to probabilistic forecasts we state two theorems that motivate the use of projections for point forecast reconciliation. First, let ${\bm \mu}_{t+h|t}:=E({\bm y}_{t+h}|{\bm y}_{1},\dots,{\bm y}_{t})$ and assume $\hat{\bm y}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.

\begin{theo}[Unbiasedness preserving property]
  For unbiased $\hat{\bm y}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection
\end{theo}
\begin{proof}
	The expected value of the reconciled forecast is given by
	\begin{align*}
	E_{1:t}\left(\tilde{\bm y}_{t+h|t}\right)&=E_{1:t}\left({\bm S}{\bm G}\hat{\bm y}_{t+h|t}\right)\\
	&={\bm S}{\bm G}E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)\\
    &={\bm S}{\bm G}{\bm \mu}_{t+h|t}\\
	\end{align*}
	Since the aggregation constraints hold for the true data generating process ${\bm \mu}_{t+h|t}$ must lie in $\mathfrak{s}$. If ${\bm S}{\bm G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range. Therefore ${\bm S}{\bm G}{\bm \mu}_{t+h|t}={\bm \mu}_{t+h|t}$ when ${\bm S}{\bm G}$ is a projection matrix.
\end{proof}
We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$. Now let ${\bm y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||{\bm v}||_2$ be the L2 norm of vector ${\bm v}$. The following theorem shows that reconciliation never increases, and in most cases reduces the sum of squared errors of point forecasts.

\begin{theo}[Distance reducing property]
	If $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ where ${\bm G}$ is such that ${\bm S}{\bm G}$ is an orthogonal projection then the following inequality holds
	  \begin{equation}
	    ||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2\le||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2
	  \end{equation}
\end{theo}
\begin{proof}
	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\mathfrak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection. Therefore
	\begin{align}
	||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2&=||({\bm S}{\bm G}\hat{\bm y}_{t+h|t}-{\bm S}{\bm G}{\bm y}_{t+h})||_2\\
	&=||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\\
	\end{align}
	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
	 \begin{equation*}
	 ||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\le
	 ||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2
	 \end{equation*}
\end{proof}
The inequality is strict whenever $\hat{\bm y}_{t+h|t}\notin\mathfrak{s}$.

@@

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation. The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast. Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
\end{figure}

@@

Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm \mu}$ and variance-covariance matrix $\hat{\bm \Sigma}$. The subscripts $t+h|t$ are suppressed for brevity. The unreconciled density

\begin{equation}
  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm y}-\hat{\bm \mu})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm y}-\hat{\bm \mu})\right]\right\}
\end{equation}

@@

\begin{equation}
f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
\end{equation}
where
\begin{equation}
q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})' \bm{\hat{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})
\end{equation}

>>>>

Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible. A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. For example, for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The \emph{bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$. For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$. The hierarchical structure of the data imply the following holds for all $t$:
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints. For the hierarchy in Figure~\ref{fig1}
$$
  \bm{S} = \begin{pmatrix}
               1 & 1 & 1 & 1  \\
               1 & 1 & 0 & 0 \\
               0 & 0 & 1 & 1 \\
               & \multicolumn{2}{c}{\bm{I}_4} &
           \end{pmatrix},
$$
where $\bm{I}_4$ is the $4\times 4$ identity matrix.

@@

It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect the inherent aggregation constraints. We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of the probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.

\begin{definition}[Coherent subspace]\label{def:cohspace}
 The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the \emph{coherent space}.
\end{definition}

It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$. Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.

\begin{figure}[H]
  \begin{center}
    \begin{tikzpicture}[
    >=stealth,
    bullet/.style={
      fill=black,
      circle,
      minimum width=1.5cm,
      inner sep=0pt
    },
    projection/.style={
      ->,
      thick,
      label,
      shorten <=2pt,
      shorten >=2pt
    },
    every fit/.style={
      ellipse,
      draw,
      inner sep=0pt
    }
    ]
    \node at (2,3) {$s$};
    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
    \node at (4.5,1.0) {$\mathfrak{s}$(image of $s$)};
    %\node[bullet,label=below:$f(x)$] at (4,2.5){};
    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
    \draw (4,2.5) ellipse (0.51cm and 1.1cm);
    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
    \end{tikzpicture}
  \end{center}
  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
\end{figure}

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  The measure $\breve{\nu}$ is coherent if it has the property
  $$
    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
  $$
\end{definition}
A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.

@@

These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom level series play an important role in the definition. However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$. For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$. In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy. However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy. The definitions above could be made in terms of any series and not just the bottom level series. In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}. Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.

@@

%Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions. According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series. Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.

@@

Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$. Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.

\begin{definition}\label{def:reconpoint}
	The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
	\begin{equation}
	  \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d}\right)\,.
	\end{equation}
\end{definition}

Many choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection. These can be defined so that $\bm{G}=\left({\bm{R}'_{\perp}}\bm{S}\right)^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$. Here, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$. For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$. In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. For this example, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method. For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations. One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$. Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$. A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while and are Table~\ref{table:2} summarises existing reconciliation methods.

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}. Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm{W}}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{figure}
	\input{Figs/pointforerec_schematic.tex}
	\caption{Summary of probabilistic point reconciliation. The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}$ onto $\mathfrak{s}$. Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
\end{figure}

@@

Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$. For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$. \citet{Wickramasuriya2017} while MinT
minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$. Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series. As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.

@@

Before generalising the concept of point reconciliation to probabilistic forecasts we state two theorems that motivate the use of projections for point forecast reconciliation. First, let $\bm{\mu}_{t+h|t}:=E(\bm{y}_{t+h}|\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.

\begin{theo}[Unbiasedness preserving property]
  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection
\end{theo}
\begin{proof}
	The expected value of the reconciled forecast is given by
	\begin{align*}
	E_{1:t}\left(\tilde{\bm{y}}_{t+h|t}\right)&=E_{1:t}\left(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\right)\\
	&=\bm{S}\bm{G}E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)\\
    &=\bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
	\end{align*}
	Since the aggregation constraints hold for the true data generating process $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$. If $\bm{S}\bm{G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range. Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
\end{proof}
We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$. Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||\bm{v}||_2$ be the L2 norm of vector $\bm{v}$. The following theorem shows that reconciliation never increases, and in most cases reduces the sum of squared errors of point forecasts.

\begin{theo}[Distance reducing property]
	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$ where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection then the following inequality holds
	  \begin{equation}
	    ||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2\le||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2
	  \end{equation}
\end{theo}
\begin{proof}
	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
	\begin{align}
	||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2&=||(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})||_2\\
	&=||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\\
	\end{align}
	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
	 \begin{equation*}
	 ||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\le
	 ||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2
	 \end{equation*}
\end{proof}
The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation. The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast. Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
\end{figure}

@@

Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$. The subscripts $t+h|t$ are suppressed for brevity. The unreconciled density

\begin{equation}
  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}
\end{equation}

@@

\begin{equation}
f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
\end{equation}
where
\begin{equation}
q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})' \bm{\hat{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})
\end{equation}
